\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{titlesec}

\renewcommand{\thesection}{\Roman{section}}
\titleformat{\section}
{\normalfont\Large\bfseries}{ARTICLE \thesection}{1em}{}

\title{AMENDED BYLAWS of ENGLISH MEADOWS HOMEOWNERS ASSOCIATION, INC., A Virginia Corporation}
\author{EMHOA \thanks{digitized by Derek LaHousse}}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\section{}
The name of the Corporation is ENGLISH MEADOWS HOMEOWNERS ASSOCIATION, INC., a Virginia Corporation, hereinafter referred to as the "Association."
The principal office of the corporation shall be located at its' Registered Agent's place of business, but meetings of members and directors may be held at such other places within the State of Virginia, as may be designated by the Board of Directors.

%\chapter{ARTICLE II}
\section{DEFINITIONS}
\begin{enumerate}
 \item["Association"] shall mean and refer to ENGLISH MEADOWS HOMEOWNERS ASSOCIATION, INC., its successors and assigns.
 \item["Properties"] shall mean and refer to that certain real property described in the Declaration of Covenants, Conditions and Restrictions, and such additions thereto as may hereafter be brought within the Jurisdiciton of the Association.
 \item["Lot"] shall mean and refer to any plot of land shown upon any recorded subdivision map of the Properties.
 \item["Owner"] shall mean and refer to the record owner, whether one or more persons or entities, of equitable or beneficial title (or legal title if same has merged) of any Lot.
  The Foregoing does not include persons or entities who hold an interest in any Lot merely as security for the performances of an obligation.
 \item["Declaration"] shall mean and refer to the Protective Covenants, Conditions and Restrictions applicable to the Properties recorded in the Office of the Clerk of the Court, Fauquier County, Virginia.
 \item["Member"] shall mean and refer to those persons entitled to membership as provided in the Declaration and Articles of Incorporation.
\end{enumerate}

%\chapter{ARTICLE III}
\section{MEETING OF MEMBERS}
\begin{enumerate}
 \item "Annual Meetings."
  The annual meeting of the members whall be held on a weekend during the month of APRIL at a specific date, time and location as determined by the directors.
 \item "Special Meetings."
  Special meetings of the members may be called at any time by the president or by the Board of Directors, or upon written request of the members who are entitled to vote one-fourth (1/4) of all the votes outstanding.
 \item "Notice of Meeting."
  Written notice, of each meeting of the members shall be given by, or at the direction of, the secretary or person authorized to call the meeting, by mailing or hand-delivering a copy of such notice, postage prepaid, at least 15 days before such meeting to each member entitled to vote thereat, addressed or delivered to the member's address last appearing on the books of the Association, or supplied by such member to the Association for the purpose of notice.
  Such notice shall specify the place, day and hour of the meeting, and, in the case of a special meeting, the purpose of the meeting.
 \item "Quorum."
  The presence at the meeting of members entitled to cast, or of proxies entitled to cast, one-fourth (1/4) of the votes of the membership shall constitute a quorum for any action except as otherwise provided in the Articles of Incorporation, the Covenants, or these By-Laws.
  If, however, such quorum shall not be present or represented at any meeting, the members entitled to vote thereat shall have power to adjourn the meeting from time to time, without notice other than announcement at the meeting, until a quorum as aforesaid shall be present or represented.
 \item "Proxies."
  At all meetings of members, each member may vote in person or by proxy.
  All proxies shall be in writing and filed with the secretary.
  Every proxy shall be revocable and shall automatically cease upon conveyance by member of his lot.
\end{enumerate}

%\chapter{ARTICLE IV}
\section{BOARD OF DIRECTORS: GENERAL}
\begin{enumerate}
 \item "Number."
  The affairs of this Association shall be managed by a Board of three (3) directors, who shall be members of this Association.
 \item "Term of Office."
  At each annual meeting the members shall elect replacement directors for terms of approximately one year and whose terms begin at the conclusion of the annual meeting.
 \item "Removal."
  Any director may be removed from the Board, with or without cause, by a majority vote of the members of the Association.
  In the event of death, resignation or removal of a director, his/her successor shall be selected by the remaining members of the Board and shall serve for the unexpired term of his/her predecessor.
 \item "Compensation."
  No director shall receive compensation for any service, with the exception of professional services, he may render to the Association as authorized by a three-fourth (3/4) majority vote of the membership.
  However, any director may be reimbursed for his actual expenses incurred in the performance of his duties.
 \item "Action Taken Without a Meeting."
  The directors shall have the right to take any action in the absence of a meeting which they could take at a meeting by obtaining written approval of all the directors.
  Any action so approved shall have the same effect as though taken at a meeting of the directors.
\end{enumerate}

%\chapter{ARTICLE V}
\section{NOMINATION AND ELECTION OF DIRECTORS}
\begin{enumerate}
 \item "Nomination."
  Nomination for election to the Board of Directors may be made by any member at any appropriate time.
  Nominations may also be made from the floor at the annual meeting subject to procedural rules adopted by the Board, if any.
  Such rules shall not be established so as to exclude any member desiring to be a candidate or desiring to submit the name of a candidate from so doing.
 \item "Election."
  Election to the Board of Directors shall be by secret written ballot if there are more than three (3) candidates on the ballot.  At such election the memberse or their proxies may cast, in respect to each vacancy, one vote each.
  The persons receiving the largest number of votes shall be elected.
  Cumulative voting is not permitted.
\end{enumerate}

%\chapter{ARTICLE VI}
\section{MEETINGS OF DIRECTORS}
\begin{enumerate}
 \item "Regular Meetings."
  Regular meetings of the Board of Directors shall be at the discretion of the Board as to time, place, frequency and manner of notice as may be fixed from time to time by mutual agreement of the Directors.
 \item "Special Meetings."
  Special meetings of the Board of Directors shall be held when called by the president o fthe Association, or by any two directors, after not less than three (3) days notice to each director.
 \item "Quorum." A majority of the number of directors shall constitute a quorum for the transaction of business.
  Every act or decision done or made by a majority of the directors present at a duly held meeting at which a quorum is present shall be regarded as the act of the Board.
\end{enumerate}

%\chapter{ARTICLE VII}
\section{POWERS AND DUTIES OF THE BOARD OF DIRECTORS}
\begin{enumerate}
 \item "Powers."
  The Board of Directors shall have the power to:
  \begin{enumerate}
   \item enforce the covenants, restricitons, easements, conditions, agreements and liens provided in the Declaration;
   \item exercise for the Association all powers, duties and authority vested in or delegated to this Association and not reserved to the membership by either provisions of these By-Laws, the Articles of Incorporation, or the Declaration; and
   \item declare the office of a member of the Board of Directors to be vacant in the event such member shall be absent from three (3) consecutive regular meetings of the board of Directors.
  \end{enumerate}
 \item "Duties."
  It shall be the duty of the Board of Directors to:
  \begin{enumerate}
   \item cause to be kept a complete record of all its acts and corporate affairs and to present a statement thereof to the members at the annual meeting of the members, or at any special meeting when such statement is requested in writing by one-fourth (1/4) of the members who are entitled to vote;
   \item supervise all officers, agents and employees of this Association, and to see that their duties are properly performed;
   \item prepare annual budget;
   \item as more fully provided in the Declaration, to:
   \begin{enumerate}
    \item send written notice of the amount of the annual assessment to every Owner subject thereto at least thirty (30) days in advance of each annual assessment period; and
    \item cause the Association to bring an action at law against the Owner personally obligated to pay the same, or foreclose the lien against the property for which assessments are not paid within thirty (30) days after the due date;
    \item cause the Assoication to provide for maintenance of the community properties and facilities;
    \item issue, or to cause an appropriate officer to issue, upon demand by any person, a certificate setting forth whether or not any assessment has been paid.
     A reasonable charge may be made by the Board for the issuance of these certificates.
     If a certificate states that an assessment has been paid, such certificate shall be conclusive evidence of such payments.
   \end{enumerate}
   \item cause the rights-of-way, easements, common areas and openspaces to be maintained
   \item procure and maintain adequate liability and hazard insurance on property owned by the Assoication;
   \item cause all officers or employees having fiscal responsibilities to be bonded, as it may deem appropriate.
  \end{enumerate}
\end{enumerate}

%\chapter{ARTICLE VIII}
\section{OFFICERS AND THEIR DUTIES}
\begin{enumerate}
 \item "Enumeration of Officers."
  The officers of this Association shall be a president and vice-president, who shall at all times be members of the Board of Directors, a secretary, a treasurer, and other such offiers as the Board may from time to time by resolution create.
 \item "Election of Officers."
  The election of officers shall take place at the first meeting of the Board of Directors following each annual meeting of the members.
 \item "Term."
  The officers of this Association whall be elected annually by the Board and each shall hold office for approximately one year unless he/she shall sooner resign, or shall be removed, or otherwise disqualified to serve.
 \item "Special Appointments." \label{itm:offices}
  The Board may elect such other officers as the affairs of the Assoication may require, each of whom shall hold office for such period, have such authority and perform such duties as the Board may, for time to time determine.
 \item "Resignation and Removal."
  Any officer may be removed from office with or without cause by the Baord.
  Any officer may resign at any time giving written notice to the Board, the president or the secretary.
  Such resignation shall take effect on the date of receipt of such notices or at any later time specified therein, and unless otherwise specified therein, the acceptance of such resignation shall not be necessary to make it effective.
 \item "Vacancies."
  A vacancy in any office may be filled by appointemnt by the Board.
  The officer appointed to such vacancy shall serve for the remainder of the term of the officer he/she replaces.
 \item "Multiple Offices."
  The offices of secretary and treasurer may be held by the same person.
  No person shall simultaneously hold more than one of any of the other offices except in the case of special offices created pursuant to \ref{itm:offices} of this Article. 
 \item "Duties."
  The duties of the officers are as follows:
  \begin{itemize}
   \item[PRESIDENT]
    The president shall preside at all meetings of the Voard of Directors; shall see that orders and resolutions of the Board are carried out; shall sign all leases, mortgages, deeds and other written instruments and shall co-sign all promissory notes and checks from such accounts as the Board may from time to time determine.
    He/she shall make appointements of Committee Chairpersons of all Standing Committees.
   \item[VICE-PRESIDENT]
    The vice-president shall act in the place and stead of the President in the event of his absence, inability or refusal to act, and shall exercise and discharge such other duties as may be required of him/her by the Board.
   \item[SECRETARY]
    The secretary shall record the votes and keep the minutes of all meetings and proceedings of the Board and of the members; keep the corporate seal of the Assoication and affix it on all papers requireing said seal; serve notice of meetings of the Board and of the members; keep appropriate current records showing the members of the Association together with their addresses, and shall perform such other duties as required by the Board.
   \item[TREASURER]
    The treasurer shall receive and deposit in appropriate bank accounts all monies of the Association and shall disburse such funds as directed by resolution of the Board of Directors; shall co-sign promissory notes and checks from such accounts as the Board may from time to time determine; keep proper books of account, cause an annual audit of the Association books to be made by an Audit Committee consisting of two persons, other than the current directors or their family; and shall prepare an annual budget and a statement of income and expenditures to be presented to the membership at its regular annual meeting, and deliver a copy of each to the members,
  \end{itemize}
\end{enumerate}

%\chapter{ARTICLE IX}
\section{INDEMNITY OF OFFICERS AND DIRECTORS}
Each Director and Officer shall be indemnified by the Corporation against liabilities, fines, penalties and claims imposed upon or asserted against him/her (including amounts paid in settlement) by reason of having been such a Director or Officer, whether or not then continuing so to be, and against all reasonable expenses (including counsel fees) incurred by him/her in connection therewith, except in relation to matters as to which he/she shall have been finally adjudged to be liable by reason of having been guilty of gross negligence or willful misconduct in th eperformance of his/her duty as such Director or Officer.
In the event of any other judgement against such Director or Officer or in the event of a settlement, the indemnification shall be made only if the Corporation shall be advised, in case none o fthe persons involved shall be or have been a Director of the Corporation, by the Board of Directors, that in its or his/her opinion such Director or Officer was not guilty of gross negligence or willful misconduct in the performance of his/her duty, and, in the event of a settlement, that such settlement was, or if still to be made is, in the best interests of the Corporation.
If the determination is to be made by the Board of Directors, it may rely, as to all questions of law, on the advice o findependent counsel.
Every reference herein to Director or Officer shall include every Director or Officer or former Director or Officer of the Corporation and every person who may have served at its request as a Director or Officer of another corporation in which the Corporation owns shares of stock or of which it is a creditor or, in case of non-stock corporation, to which the Corporation contributes and, in all of such cases, his/her executors and administrators.
The right of indemnification hereby provided shall not be exclusive of any other rights to which any Director or Officer may be entitled.

%\chapter{ARTICLE X}
\section{COMMITTEES}
The Board of Directors shall appoint an Architectural Review Committee and other committees as deemed appropriate in carrying out its purpose.

%\chapter{ARTICLE XI}
\section{BOOKS AND RECORDS}
The books, records and papers of the association shall at all times, during reasonable hours, be subject to inspection by any member.
The president and/or secretary shall have available for purchase as reasonable cost the Declaration, the Articles of Incorporation and the By-Laws of the Association.

%\chapter{ARTICLE XII}
\section{ASSESSMENTS}
\begin{enumerate}
 \item "Due Date."
  Assessments shall be due on March 1st of every year.

\end{enumerate}

\section{*MISSING*}
TODO Missing sections article 13 and 14 from page 10

\section{*MISSING, budget?*}
... Year (at the annual meeting).
The approved budget will be assessed equally to the members.

%\chapter{ARTICLE XV}
\section{AMENDMENTS}
\begin{enumerate}
 \item "Amendments."
  These By-laws may be amended, at a regular or special meeting of the members, by a vote of a majority of a quorum of members present in person or by proxy.
 \item "Conflict Between Documents."
  In case of any conflict between the Articles of Incorporation and by these By-laws, the Articles shall control; and in the case of any conflict between the Declaration and these By-laws, the Declaration shall control.
\end{enumerate}

%\chapter{ARTICLE XVI}
\section{FISCAL YEAR}
The fiscal year of the Association shall begin on the first day of January and end on the 31st day of December of every year.

%\section*{}
IN WITNESS WHEREOF, we being all the Directors of ENGLISH MEADOWS HOMEOWNERS ASSOCIATION, INC. have hereunto set our hands this 21st day of September, 1995.
\begin{itemize}
 \item J. S. BAKEWELL, DIRECTOR
 \item T. C. McDERMOTT, DIRECTOR
 \item D. SOBOTKA, DIRECTOR
\end{itemize}
\end{document}
