\documentclass[10pt, letterpaper]{article}
\usepackage{enumitem}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}

\title{ENGLISH MEADOWS SUBDIVISION PROTECTIVE COVENANTS,\linebreak[0] CONDITIONS AND RESTRICTIONS}
\author{EMHOA \thanks{digitized by Derek LaHousse}}
\date{\today}

\setlist[enumerate]{itemsep=0mm}
\begin{document}
%\maketitle
%\tableofcontents

\begin{abstract}
  Sentry Realty, Inc. hereinafter called ``Declarant'' is the owner in fee simple of certain real property located in Fauquier County, Virginia and know by official plat designation as ENGLISH MEADOWS SUBDIVISION; recorded among the land records of Fauquier County, Virginia.

  For the purpose of enhancing and protecting the value, attractiveness and desirability of the lots or tracts constituting such subdivision, (this subdivision having been authorized by Special Exception Permit granted by the Fauquier County Board of Supervisors on the 15th day of July, 1986) the Declarant hereby declares that all of the real property described above and each part thereof shall be held, sold, and conveyed only subject to the following easements, covenants, conditions, and restrictions, which shall constitute covenants running with the land and shall be binding on all parties having any right, title or interest in the above-described property or any part thereof, their heirs, successors, and assigns, and shall inure to the benefit of each owner thereof.
\end{abstract}

\section{DEFINITIONS}
\begin{itemize}
  \item ``Declarant'' shall mean Sentry Realty, Inc., and its successors, and assigns.
  \item ``Association'' shall mean and refer to ENGLISH MEADOWS HOMEOWNERS ASSOCIATION, INC., a non-stock Virginia corporation, successors and assigns.
  \item ``Member'' shall mean every person or entity who holds membership in the Association.
  \item ``Owner'' shall mean the record holder, whether one or more persons or entities, of a fee simple title to any lot which is part of the property.
  \item ``Subdivision'' shall mean the entire real property herein-above described and subdivided into lots, streets, common areas, and known by official plat designation as ENGLISH MEADOWS SUBDIVISION, SECTION I, according to plat of subdivision thereof, to be recorded in the Clerk's office of the Circuit Court of Fauquier County, Virginia.
    It is contemplated by Declarant that additional lands shall be subdivided into subsequent Sections of English Meadows, in which event each lot and lot owner shall be subject to the matters set out herein and become a member of English Meadows Homeowners' Association, Inc., respectively.
  \item ``Lot'' shall mean any plot of land shown as a residential building lot on the recorded subdivision plat referred to above.
    Common areas, streets and well lot are not included.
  \item ``Common Area'' shall mean all real property owned by the Association for the common use and enjoyment of its owners, sometimes referred to ``Common Open Space''
    The common area to be owned by the Association is described and designated on the plat of subdivision of English Meadows.
    Declarant to retain Non Common Open Space.
  \item ``Non-Common Areas'' shall mean all of the property shown on said plat not included in lots, streets or common areas which ``Non-common Areas'' are reserved by the Declarant.
    ``Non-Common Areas'' are specifically exempt from the operation and effect of these Protective Covenants, Conditions and Restrictions, and shall be deed restricted for use only for agriculture purposes for a period of 25 years or less from date of plat approval by the Board of Supervisors, unless the use thereof of the further subdivision thereof is approved by the Fauquier County Board of Supervisors or the governing body having land use jurisdiction over said ``Non-Common Area'' pursuant to ordinance.
\end{itemize}

\section{ASSOCIATION}
Every owner of a lot shall be a member of the ENGLISH MEADOWS HOMEOWNERS ASSOCIATION, INC., a non-stock Virginia Corporation.
Membership shall be appurtenant to and may not be separated from ownership of a lot.
\begin{enumerate}
  \item[Membership] The Association shall have two classes of voting members as follows:
    \begin{itemize}
      \item[Class A.] Class A members shall be all owners with the exception of Declarant and shall be entitled to One (1) vote for each lot owned.
        When more than one person holds an interest in a given lot, such person or persons shall be members and the vote for each lot shall be exercised as they may determine among themselves.
        In no event shall more than one vote be cast with respect to any lot owned by Class A members.
      \item[Class B.] The Class B member shall be the Declarant who shall be entitled to exercise Three (3) votes for each lot owned.
        The Class B membership shall cease and be converted to a Class A membership when the total votes outstanding in the Class A membership equals the total votes outstanding in the Class B membership.
    \end{itemize}
  \item[Funding] In order to provide initial operating capital for the Association, each new home purchaser of a lot in the Subdivision, upon acceptance from the builder of a deed for his lot, shall pay \$20.00 into the treasury of the Association.
    Thereafter, the Association shall be funded by the levying of regular and special assessments as hereinafter provided.
  \item[Board of Directors] The membership shall elect by simple majority the Associations Board of Directors whose responsibility it shall become to conduct all necessary business on behalf of the Association, including but not limited to:
    \begin{enumerate}
      \item administration of the Association accounts,
      \item fixing of regular assessments and their method of collection,
      \item payment of real estate taxes applicable to the common areas,
      \item maintenance of insurance policies to provide liability coverage as to the common areas.
    \end{enumerate}
\end{enumerate}

\section{ASSESSMENTS}
Declarant hereby covenants for each lot within the subdivision, and each owner of a lot, by acceptance of his deed for said lot, is hereby deemed to covenant to pay to the Association any and all assessments levied by the Association as hereinafter provided.

There shall be two types of assessments.

\begin{enumerate}
  \item[Regular Assessments] Regular assessments shall be established by the Association's Board of Directors as to their amount and method of collection and may be adjusted by the Board of Directors on an annual basis depending on the financial need of the Association.

    Regular assessments are hereby fixed at \$30.00 every six months for each lot until such time as a different rate is established by the Board of Directors.
    The first regular assessment accruing to each lot shall be prorated from the first day of the month following the delivery of the deed of said lot.
    The association may, by a vote of two-thirds of the owners of the lots within the Subdivision, direct its Board of Directors to increase the amount of the regular assessment to include the cost for garbage and rubbish removal service for all lots.
  \item[Special Assessments] In addition to the regular assessments authorized above, the Association may levy a special assessment or assessments for the purpose of defraying, in whole or in part, the cost of any construction, repair or replacement of a capital improvement on the common area or streets including fixtures and personal property related thereto.
    Such special assessments shall be limited to one per year and each such special assessment must be approved by a vote of two-thirds of the owners of the lots within the Subdivision.

    Both regular and special assessments shall be further governed as follows:
    \begin{enumerate}
      \item All assessment funds shall be used exclusively to promote the health, safety, welfare, and recreation of the residents in the Subdivision and for the improvement and maintenance of the common areas.
      \item Each assessment must be fixed at the same rate and method of collection for all lots within the Subdivision.
      \item Written notice of all assessments shall be sent to every owner subject thereto at least 30 days before that assessment becomes due and payable.
      \item Any assessment not paid within 15 days after its due date shall be deemed in default and shall bear interest from its due date at the then current legal rate of interest.
      \item Each assessment, together with any applicable interest costs of reasonable attorney's fees, shall be the personal obligation of the person or persons who owned the lot at the time of the assessment fell due and shall be a charge on the land and a continuing lien on the lot against which such an assessment is made.
        Said assessment lien shall be subordinate to the lien of any mortgage or deed of trust.
      \item The Association may bring an action at law against any owner in default or may foreclose the lien against the property.
      \item The Association shall on or before January 15 of each year cause to be recorded in the office of the Clerk of the Circuit Court of Fauquier County, a list of owners in default and delinquent assessments as of that date.
      \item The Association shall, on demand and for a reasonable charge, furnish a certificate signed by an officer of the Association setting forth the then current status of a specific lot as to the payment of assessments levied against that lot.
      \item No owner may waive or otherwise escape liability on assessments provided for herein by non-use of the common area, abandonment of his lot, or for any other reason whatsoever.
    \end{enumerate}
\end{enumerate}

\section{PROPERTY RIGHTS/COMMON AREA}
\begin{enumerate}
  \item Every owner of a lot shall have a right and easement of enjoyment for passive recreation in and to the common area and active recreation as approved by the Association.
    Said right shall be appurtenant to and shall pass with the title to such lot, subject to reasonable rules and regulations as may be established from time to time by the Association.
  \item Subject to such limitations as may be imposed by the by-laws, each owner may delegate his right of enjoyment in and to the common areas to the members of his family, his guests, tenants and invitees.
  \item There shall be no judicial partition of the common area, nor shall Declarant, or any owner or any other person acquiring any interest in the subdivision or any part thereof, seek judicial partition thereof.
    However, nothing contained herein shall be construed to prevent judicial partition of any lot owned in co-tenancy.
  \item Clearing in the common area shall be restricted to underbrush and/or dead and felled trees.
    Except for the common areas carrying running water which areas are to be maintained as a state of nature easement for a minimum distance of 50 ft. on each side of said running water.
  \item The BMP pond or berms in common area is to be maintained by the Association in strict accordance with the standards and provisions of Article II-602 of the Fauquier County Zoning Ordinance adopted May 19, 1981, as amended.
  \item No lands in common open space shall be denuded, defaced or otherwise disturbed in any manner at any time without the approval of the Director.
  \item \begin{enumerate}
      \item In the event the Association, or any successor organization, shall at any time after establishment of the development fail to maintain the common space/improvements in reasonable order and condition in accordance with the approved plans, the County may serve notice in writing upon such organization or upon the residents of the development setting forth the manner in which the organization has failed to maintain the common open space/improvements in reasonable condition, and said notice shall contain a demand that such deficiencies of maintenance be cured within thirty (30) days thereof, and shall state the date and place of a public hearing thereon which shall be held within twenty (20) days of the notice.
      \item At such a hearing the County may modify the terms of the original notice as to the deficiencies and may grant an extension of time within which they shall be cured.
      \item If the deficiencies set forth in the original notice or in the modifications thereof shall not be remedied within said thirty (30) days or an extension thereof, the County, in order to preserve the taxable values of the properties within the development and to prevent the common open space/improvements from becoming a public nuisance, may enter upon said common open space and maintain the same for one (1) year.
      \item Said entry and maintenance shall not vest in the public any rights to use the common open space/improvements except when the same is voluntarily dedicated to the public by the owners.
      \item Before the expiration of said one (1) year period, the County shall, upon its initiative or upon the request of the organization theretofore responsible for the maintenance of the common open space/improvements, call a public hearing upon notice in writing to such organization or to the residents of such development, to be held by the Board, at which hearing the organization shall show cause why such maintenance by the County shall not continue for a succeeding one (1) year period.
      \item If the Board shall determine that such organization is ready and able to maintain the common open space/improvements in reasonable condition, the County shall cease to maintain the common open space/improvements at the end of said one (1) year period.
      \item If the Board shall determine that such organization is not ready and able to maintain the common open space/improvements in a reasonable condition, the County may, in its discretion, continue to maintain the common open space/improvements during the succeeding year, subject to a similar hearing and determination in each year thereafter.
      \item The cost of such maintenance by the County shall be assessed ratably against the properties within the development that have a right of enjoyment of the common open space/improvements, and shall become a charge of said properties, and such charge shall be paid by the owner of said properties within thirty (30) days after receipt of a statement thereto.
    \end{enumerate}
\end{enumerate}

\section{EASEMENTS}
\begin{enumerate}
  \item Declarant reserves for itself, its successors and assigns, an easement for ingress and egress across common properties.
  \item Declarant further reserves for themselves, their successors and assigns, until December 31, 1995, the right to grant easements for the installation and maintenance of utilities and drainage facilities across the lots and parcels in the subdivision as Declarant may deem reasonable necessary, provided the Declarant's lienors hereto approve, which approval they shall not be required to give
  \item Easements are reserved on and across all common open space area in the subdivision for the benefit of the Association for the purpose of such maintenance activities as the Association shall undertake.
\end{enumerate}

\section{CENTRAL WATER SYSTEMS}
It is the intent of Declarant to construct or have constructed a central water system for supply of water to all dwellings within the subdivision.
Said central water system to be constructed to applicable standards as set by the Commonwealth of Virginia, Department of Health and applicable standards of the Fauquier County Water and Sanitation Authority.
Upon completion of said water system and its approval by the Department of Health, Declarant is to transfer ownership of the entire central water system to the Fauquier County Water and Sanitation Authority (WSA).
Upon acceptance of the system by WSA, Declarant will relinquish to WSA all responsibility and liability for operation and maintenance of the central water system.

In the event that the Fauquier County Water and Sanitation Authority refuses to accept the central water system, the Association shall operate said system under the identity of the English Meadows Homeowners Association, Inc., and shall have sole ownership of said system and shall receive all fees charged to homeowners for water services.
Said fees may be adjusted from time to time to cover operating costs.

\section{ROADS AND STREETS}
Declarant shall be responsible for the design and construction of all public streets as shown on the recorded plat of Subdivision.
Said design and construction to be applicable standards as set by the Commonwealth of Virginia, Department of Transportation (VDOT).

Declarant shall post bond or provide letter of credit to insure completion of said street to State standards with the amount of the bond to be determined by Fauquier County Planning Office.

Upon completion of construction and acceptance by VDOT, Declarant shall petition the Fauquier County Board of Supervisors for inclusion of said streets into the County's public road system.
Prior to acceptance of said streets into the Fauquier County public road system, Declarant shall be responsible for keeping streets in a passable and usable condition.

Declarant, however, is not responsible for damage to roads, ditches, or culvert pipes, or the tracking of mud and debris onto streets as a result of construction on a lot or lots.
Individual lot owners shall be responsible for any such damage resulting from construction on their lot or lots.
Should such damage occur the repair of which is necessitated by Fauquier County or VDOT, the lot owner will be given written notice to repair such damage at his own expense.
If said damage is not repaired within fourteen (14) days of notice, Declarant may perform the same, and thereupon place a lien on the land for the cost of same, which lien shall be subordinate only to taxes or deeds of trust.

Common driveways are to be jointly maintained by the owners of all lots served by said common driveway.

\section{USE RESTRICTIONS}
The subdivision shall be occupied and used only as follows:
\begin{enumerate}
  \item Each lot shall be used as a residence for a single family and for no other purpose
  \item No business of any kind shall be conducted on any residence with the exception of the business of Declarant and the transferees of Declarant in developing all of the lots as provided herein.
  \item No noxious or offensive activities shall be carried on, in or on any lot with the exception of the business of Declarant and the transferees of Declarant in developing all of the lots as provided herein.
  \item No sign of any kind shall be displayed to public view on a lot or common area without the prior written consent of the Association, except customary name and address signs and lawn signs of not more than five square feet in size advertising a property for rent or sale.
  \item Nothing shall be done or kept on a lot or on the common area which would increase the rate of insurance relating thereto without the prior written consent of the Association, and no owner shall permit anything to be done or kept on his lot or the common area which would result in the cancellation of insurance on any residence or on any part of the common area, or which would be in violation of any law.
  \item No animals, livestock, or poultry of any kind shall be raised, bred, or kept on any lot (farmette excepted) or on the common area.
    However, dogs, cats and other household pets may be kept on lots subject to such rules and regulations as may be adopted by the Association, so long as they are not kept, bred, or maintained for commercial purposes.
  \item No rubbish, trash, or garbage or other waste materials shall be kept or permitted on any lot or on the common area except in sanitary containers located in appropriate areas concealed from public view.
  \item No fence, hedge, wall, or other dividing instrumentality shall be constructed or maintained on any lot except upon approval of the Architectural Committee as provided herein.
  \item No outbuilding, basement, tent, shack, garage, trailer, shed or any temporary building of any kind shall be used as a residence, either temporarily or permanently.
  \item No building shall be erected, placed, or altered on any building lot in this subdivision until the building plan specifications, and plat plans showing the location of such building have been approved in writing as to conformity and harmony of external design with existing structures in the subdivision and as to location of the building with respect to topography and finished ground elevation by the Architectural Committee to be selected by Declarant.
    All such approvals shall be determined by said Architectural Committee, in its sole discretion, and no member of the Association, jointly or in concert, shall have any recourse from any determination of said Architectural Committee.
  \item Each residential dwelling shall have a minimum of 1,800 square feet of finished living area.
    However, in the case of a dwelling of more than one level, the ground floor shall have a minimum of 1,000 square feet of said finished living area.
    However if an attached (not built-in) garage of at least 400 square feet is constructed, said square feet may be reduced to 1,500 square feet for one level rambler and 800 square feet on ground level if more than one level dwelling.
  \item No repair work or disassembling of automobiles will be permitted, except such minor repair work as is commonly performed by the typical automobile owner.
  \item The owners of each lot shall be responsible for maintaining the driveway or culvert giving that owner access to the State maintained road, within the boundaries of their respective lots in good condition and repair, using the same type of materials employed in the original construction and surfacing of the driveways and culverts.
  \item All telephone, electric and other utility lines and connections between the main utility lines and the residences or other buildings on each lot shall be concealed and located underground so as not to be visible.
  \item The septic system will be installed in complete compliance with Fauquier County Health Department and all subservice drainfields for individual sewage disposal systems shall be located on each lot as shown on the lot certification plan for ENGLISH MEADOWS SUBDIVISION, as prepared by James Harris \& Associates, and approved by the Fauquier County Health Department.
    However lot owner may apply to Fauquier County Health Department at his expense for revision and if approved by said Health Department, may make such revision provided it does not interfere with adjacent lots.
\end{enumerate}

\section{GENERAL PROVISIONS}
\begin{enumerate}
  \item Declarant, the Association, or any owner shall have the right to enforce, by any proceeding at law, or in equity, all restrictions, conditions, covenants, easements, reservations, liens, and charges now or hereafter imposed by the provisions of this declaration.
    Failure by Declarant, the Association, or any owner to enforce any covenant or restriction herein contained shall in no event be deemed a waiver of the right to do so thereafter, and each member of the association, by his acceptance of the deed of conveyance of his lot, acknowledges that he has received and read a copy of these Protective Covenants and Restrictions, and hereby, for himself and on behalf of his heirs, successors and assigns forever waives and relinquishes any right of action he may have, or which may hereinafter accrue, jointly or in convert with other members, against the Declarant, the Architectural Committee or the Board of Directors of the Association, or the individual members thereof for any failure to enforce any of the Covenants and/or Restrictions set out herein.
  \item Invalidation of any one of these covenants or restrictions by judgment or court order shall in no way effect any other provision, which shall remain in full force or effect.
  \item Covenants and restrictions of this declaration may be amended by duly recording an instrument executed and acknowledged by not less than three-quarters of the Association membership votes.
  \item No breach of any conditions herein contained or reentry by reason of such breach shall defeat or render invalid the lien of any mortgage made in good faith, and for the value as to the subdivision or any lot therein; provided, however, that such conditions shall be binding on any owner whose title is acquired by foreclosure, trustee sale, or otherwise.
  \item The covenants and restrictions of this declaration shall run with and by the land and shall inure to the benefit of and be enforceable by the Association or a member thereof for a period of twenty-five years from the date hereof, unless otherwise approved by the Fauquier County Board of Supervisors or the governing body of local jurisdiction, and thereafter shall continue automatically in effect for additional periods of twenty-five years, unless otherwise agreed to in writing by the then owners of at least three-quarters of the subdivision lots.

    Special Exception approved under old ordinance.
\end{enumerate}

\section{NOTARIZATION}
Signatures and seals omitted
\end{document}
